Parallel Computations for Solving Multicriteria Mixed-Integer Optimization Problems

### 2021-02-08 2021/PСT_GergelKozinov/2021_PCT.tex
1 \omega -> \Omega

Assume that 
\begin{equation}\label{eq:13}
 \omega_k=\{ y^i,u^i,z^i=F(\alpha,y^i,u^i ): 1\leq i\leq k \}
\end{equation}
is the search information obtained in the process of calculation after $k>1$ global search iterations. Then the procedure for adaptive estimation of the discrete parameter value, at which the minimum value  of the function $F(\alpha,y,u)$ is expected to be obtained, can be determined using the decision rule
\begin{equation}\label{eq:14}
	\theta =\Theta(\omega_k ),1 \leq \theta \leq l, 
\end{equation}
 that determines the most promising value of the discrete parameter $u \in U$ at each step of the global search.

@@

\textit{Rule 1.} Apply the decision rule $\Theta$ from (\ref{eq:14}) to available search information $\omega_k$ from (\ref{eq:13}),  and determine the value of the discrete parameter $u=w_\theta$, $w_\theta \in U$.

@@

\textit{Rule 3.} Check the stopping condition for the computation. If the required accuracy of the global search is not achieved, it is necessary to supplement the search information $\omega_k$ from (\ref{eq:13}) with the results of the current iteration and continue calculations starting from Rule 1.

@@

It should be noted that the computational complexity of solving global optimization problems increases exponentially with increasing dimensionality. The problem of increasing computational complexity was even called the ``dimensionality curse''. In particular, when applying the computational scheme discussed in subsection \ref{subsec:31}, it is necessary to accumulate and analyze multidimensional search information $\omega_k$ from (\ref{eq:13}). This computational complexity can be significantly reduced by reducing the optimization problems to be solved by using Peano \textit{curves} or \textit{evolvents} $y(x)$, which unmbiguously and continuously map a segment [0,1] on an $n$-dimensional hyper-cube $D$ -- see, for example, \cite{c24,c25}. As a result of this reduction, the multidimensional global optimization problem (\ref{eq:6}) is reduced to a one-dimensional problem
\begin{equation}\label{eq:15}
 \min_{y\in D, u \in U}F(\alpha,y,u) = \min_{x \in [0,1]}(F(\alpha,y(x),w_1 ),F(\alpha,y(x),w_2 ),\dots,F(\alpha,y(x),w_l ))
\end{equation}

@@

As a result of dimensionality reduction, the search information $\omega_k$ from (\ref{eq:13}) obtained in the calculation can be presented in the form 
\begin{equation}\label{eq:17}
A_k=\{(x_i, u_i, z_i, f_i = f(y(x_i), u_i): 1 \leq i \leq k \},
\end{equation}
where $x_i$, $u_i$, $1 \leq i \leq k$,  are the points of the global search iterations, $z_i$, $f_i$, $1 \leq i \leq k$,  are the values of the scalar criterion $F(\alpha,y(x),u)$ and the criteria $f_i (y)$, $1 \leq i \leq s$, calculated at the points $x_i$, $u_i$, $1 \leq i \leq k$. Note that the data in the set $A_k$ are arranged in ascending order\footnote{Data ordering is reflected by using a subscript.} of the points $x_i$, $1 \leq i \leq k$, i.e.
\begin{equation}\label{eq:18}
 x_1< x_2< \dots < x_k
\end{equation}
for a more efficient execution of global search algorithms.

>>>>

Assume that 
\begin{equation}\label{eq:13}
 \Omega_k=\{ y^i,u^i,z^i=F(\alpha,y^i,u^i ): 1\leq i\leq k \}
\end{equation}
is the search information obtained in the process of calculation after $k>1$ global search iterations. Then the procedure for adaptive estimation of the discrete parameter value, at which the minimum value  of the function $F(\alpha,y,u)$ is expected to be obtained, can be determined using the decision rule
\begin{equation}\label{eq:14}
	\theta =\Theta(\Omega_k ),1 \leq \theta \leq l, 
\end{equation}
 that determines the most promising value of the discrete parameter $u \in U$ at each step of the global search.

@@

\textit{Rule 1.} Apply the decision rule $\Theta$ from (\ref{eq:14}) to available search information $\Omega_k$ from (\ref{eq:13}),  and determine the value of the discrete parameter $u=w_\theta$, $w_\theta \in U$.

@@

\textit{Rule 3.} Check the stopping condition for the computation. If the required accuracy of the global search is not achieved, it is necessary to supplement the search information $\Omega_k$ from (\ref{eq:13}) with the results of the current iteration and continue calculations starting from Rule 1.

@@

It should be noted that the computational complexity of solving global optimization problems increases exponentially with increasing dimensionality. The problem of increasing computational complexity was even called the ``dimensionality curse''. In particular, when applying the computational scheme discussed in subsection \ref{subsec:31}, it is necessary to accumulate and analyze multidimensional search information $\Omega_k$ from (\ref{eq:13}). This computational complexity can be significantly reduced by reducing the optimization problems to be solved by using Peano \textit{curves} or \textit{evolvents} $y(x)$, which unmbiguously and continuously map a segment [0,1] on an $n$-dimensional hyper-cube $D$ -- see, for example, \cite{c24,c25}. As a result of this reduction, the multidimensional global optimization problem (\ref{eq:6}) is reduced to a one-dimensional problem
\begin{equation}\label{eq:15}
 \min_{y\in D, u \in U}F(\alpha,y,u) = \min_{x \in [0,1]}(F(\alpha,y(x),w_1 ),F(\alpha,y(x),w_2 ),\dots,F(\alpha,y(x),w_l ))
\end{equation}

@@

As a result of dimensionality reduction, the search information $\Omega_k$ from (\ref{eq:13}) obtained in the calculation can be presented in the form 
\begin{equation}\label{eq:17}
A_k=\{(x_i, u_i, z_i, f_i = f(y(x_i), u_i): 1 \leq i \leq k \},
\end{equation}
where $x_i$, $u_i$, $1 \leq i \leq k$,  are the points of the global search iterations, $z_i$, $f_i$, $1 \leq i \leq k$,  are the values of the scalar criterion $F(\alpha,y(x),u)$ and the criteria $f_i (y)$, $1 \leq i \leq s$, calculated at the points $x_i$, $u_i$, $1 \leq i \leq k$. Note that the data in the set $A_k$ are arranged in ascending order\footnote{Data ordering is reflected by using a subscript.} of the points $x_i$, $1 \leq i \leq k$, i.e.
\begin{equation}\label{eq:18}
 x_1< x_2< \dots < x_k
\end{equation}
for a more efficient execution of global search algorithms.
